Mitigating Interest Flooding DDoS Attacks in Named Data Networking

### 2012-12-07 eval-small-scale.tex
typo
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@872 df1a90cd-247b-4364-bdaf-287a704eb499

When routers apply a more intelligent metod to process incoming Interests (i.e., based on the incoming interface statistics), an Interest flooding attack becomes virtually ineffective.
That is, malicious Interests are simply not getting admitted to the network, not being able to create much service disturbance for the legitimate users.
The observed periodicity of the probabilistic Interest accept curve on Fig.~\ref{fig:small-scale attack progress} is a direct result from ``intelligence'' (Interest satisfaction rate statistics) decaying with time.
The 50-second periods approximately correspond to the selected exponential decaying parameter $\alpha=e^{−1.0/30.0}$, which decays statistics to $1/e$ of the initial value within 30~seconds and to $\approx20\%$ within 50~seconds.
The primary reason that such minimum peaks exist is the fact that when attack Interests start to get readmitted, they cause degradation of statistics on routers close to the producer (i.e., routers that observe traffic mix from legitimate and malicious users).
This degradation subsequently reduces chances for legitimate Interests get through (see Section~\ref{sec:probabilistic}) until malicious Interests are ``pushed back'' to the edge.

>>>>

When routers more intelligently process incoming Interests (i.e., based on the incoming interface statistics), the Interest flooding attack becomes virtually ineffective.
That is, malicious Interests are simply not getting admitted to the network, not being able to create much service disturbance for the legitimate users.
The observed periodicity of the probabilistic Interest accept curve on Fig.~\ref{fig:small-scale attack progress} is a direct result from ``intelligence'' (Interest satisfaction rate statistics) decaying with time.
The 50-second periods approximately correspond to the selected exponential decaying parameter $\alpha=e^{−1.0/30.0}$, which decays statistics to $1/e$ of the initial value within 30~seconds and to $\approx20\%$ within 50~seconds.
The primary reason that such minimum peaks exist is the fact that when attack Interests start to get readmitted, they cause degradation of statistics on routers close to the producer (i.e., routers that observe traffic mix from legitimate and malicious users).
This degradation subsequently reduces chances for legitimate Interests get through (see Section~\ref{sec:probabilistic}) until malicious Interests are ``pushed back'' to the edge.
